Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-02-24 1_manuscript/itt-emotion_V6-1.tex
Renamed a few files

  \textit{Omotenashi}, the Japanese spirit of hospitality and service, is known and studied worldwide for its excellence. In recent years, the number of international tourists, particularly Chinese tourists, to Japan has been steadily increasing. However, most studies on tourists’ behavior are biased toward the Western world. Previous research has shown that different cultural backgrounds give rise to different expectations and arguably, different satisfaction factors. To address the knowledge gap in this area, a cross-cultural study on the differences between Chinese and Western cultures in the high-standard Japanese hospitality environment is merited. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the soft attributes such as service or be more concerned with hard attributes such as location and facilities? We examine these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges. Taking advantage of the facile data gathering capability enabled by the Web 2.0 technology, we applied Shannon's entropy metric to extract these factors automatically and then used them in a support vector machine to classify a more extensive data set. We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to ``praising'' adjectives. We found that Chinese tourists are less concerned with hospitality and more with room quality than are Western tourists, whereas, the latter are delighted more by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese-friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

@@

  Japan’s hospitality has been known historically to be of the highest quality. \textit{Omotenashi}, which describes the spirit of Japanese hospitality, is celebrated worldwide. With roots in Japanese history and tea ceremony, Japanese hospitality is globally famous \cite[][]{al2015characteristics}. Therefore, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}. Thus, it could be theorized that their satisfaction factors should be different. How will different cultures react and perceive hotels and their hospitality in this context?

  In the last couple of decades, the economy of Japan has been affected by an increase in inbound international tourism \cite[][]{jones2009}. A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}. The tourist population was mostly Asian (86.14\%), and approximately one-fourth of the total (25.63\%) was from China. Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language. The effect of Chinese tourists on international economies is increasing. Consequently, the number of studies on this phenomenon has been increasing \cite[][]{sun2017}. The tourist market is gradually becoming diverse because of multicultural tourist populations. Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will be varied. Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

  However, many tourist-behavior analyses have been performed involving Western subjects. As such, a gap in knowledge existed until recent decades. In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}. Few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples. These studies, although valid, can have limitations. This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners account for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.

@@

  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to determine customer groups' satisfaction and dissatisfaction factors across several price ranges. We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings. More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction. We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, location, infrastructure, and surrounding real estate. In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.

@@

  We attempt to clarify the difference in satisfaction and dissatisfaction factors between different cultures. These factors can become the focal point for improving the tourism and service industries and increasing customer satisfaction. Satisfied customers will then write more positive online reviews that will, in turn, increase sales and attract new customers.

@@

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the country’s history, and to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}. There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that it originates even earlier, in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Presently, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training. High standards are always followed to not fall behind in the competition. In Japanese businesses, including hotels, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language,'' one of the most formal of the Japanese formality syntaxes. They are also trained to bow differently depending on the situation, where a light bow could be used to say ``Please, allow me to guide you.'' Deep bows are used to apologize for any inconvenience the customer could have faced, followed by a very respectful apology. Although the word \textit{omotenashi} can be translated directly as ``hospitality,'' it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}. This hospitality culture permeates every type of business with customer interaction in Japan. A simple convenience shop could express all of these hospitality and service standards, which are not exclusive to hotels.

@@

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}. Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. These expectations will be there from the moment that they choose the hotel throughout their stay. In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.

@@

    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious. For example, suppose a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit. In that case, they will be satisfied with this matter. However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night. In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed. Then, the same customer might have packed their toiletries, thinking that the amenities might not include those. They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation. This definition of satisfaction does not allow us to examine overall customer satisfaction. However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole. In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects. Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service. On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.

@@

    Previous research has also focused more on soft attributes, with little focus on hard attributes, such as location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}. However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.

@@

    % Asians vs. Western behavior
    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior. Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of Chinese tourism studies. This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists. To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists. One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money. Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities. At the same time, Asian tourists were more inclined to enjoy the Karaoke facilities of hotels. Both groups tend to have high expectations for the overall facilities. Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty. In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and increased knowledge as a common motivator.

    One thing to note with the above Asian vs. Western analyses is that they were performed before 2000 and that they are not Chinese specific but study Asian people in general. Meanwhile, the current Chinese economy boom is increasing the influx of tourists of this nation. The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations. In turn, if we follow the definition of satisfaction in \cite{hunt1975}, then change in expectations could have influenced their satisfaction factors when traveling. Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports. However, our study of online reviews takes the data that the hotel customers uploaded themselves. This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies. Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.

@@

    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically. Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents. In this environment, do customers hold their satisfaction to this hospitality regardless of their culture, or are other factors more relevant to the customers? Our study measures this at a large scale across different hotels in Japan.

@@

    % Studies are not universal.
    Although the studies focusing only on Chinese or Western tourists have a narrow view, their theoretical contributions are valuable. We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly. Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other. Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews. This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire. Our method allows us to find factors that we would not have contemplated. It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves. This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples. This study could also help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature.

    % Reviewer comparison table
    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and may serve to further highlight our study and its merits. A contrast is shown in Table \ref{tab:lit-rev}. This table shows that older studies were conducted with surveys and had a different study topic. These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}. However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies. Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}. One important difference is the geographical focus of their studies. While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan. The focus on Japan is important because of its top rank in hospitality across all types of businesses. This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures? Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent. The number of samples in other text-mining studies is also smaller than ours in comparison. Apart from that, every study has a different text mining method.

@@

    % Sentiment Analysis
    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies. This method is called sentiment analysis or opinion mining. A precursor of this method was attempted decades ago \cite[][]{stone1966general}. With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, a critical opinion. This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm. Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on. In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.

    % Machine Learning
    The algorithm used for sentiment analysis in our study is called a support vector machine, a form of supervised machine learning used for binary classification. This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically. Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task. Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template. Machine learning can also be unsupervised, where without any pre-labeled data. In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions. Our study calls for a supervised machine since text analysis can be intricate. Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels. Consequently, we teach the machine through previously labeled text samples.

@@

    In this study, we predict that several things might occur. Our data show satisfaction and dissatisfaction factors that are universal and strictly cultural factors. However, we expect that both of these options will present themselves. We can also assert that we could arrive at very similar results to previous literature if they are correct in their findings. However, we are using a database of several orders of magnitude larger. We can also expect to discover patterns that researchers previously had not noticed because of the lack of questionnaire design and users' freedom to record their pleasures and grievances.

@@

  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}. We then determined the most commonly used words that contribute to positive and negative opinions in a review. We did this using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers. We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC). We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews. We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels. We observed the frequency of the terms in the dataset to extract the most utilized words in either review. We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}. Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel. Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which can be changed by the staff or management. Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, and the hotel's surroundings, which are impossible to change by the staff alone.

@@

    An SVM is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space. Each dimension is a feature of the data in this space. The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes classification error.

    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below. Each training sentence is a data point, a row in the vector \(x\). Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence. The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector. The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle. The bias coefficient \(b\) determines its position.

    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data. These changes to the weight vector are greater for features close to the separating hyperplane. These features have stronger changes because they needed to be taken into account to classify with a minimal error. Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process. Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\). Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications. This equation shows the last value of \(\alpha\) after the end of the cycle.

@@

    Our research questions were related to two issues. Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine how Chinese and Western tourists respond to the \textit{omotenashi} culture, which influences hospitality and service in Japan, and the differences in their perception of this hospitality. We observed the top-ranking positive factors for Chinese tourists across different price ranges, as shown in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings, as shown in Table \ref{tab:adj_zh_pos}. These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location usually placed higher in importance on the pairings. From the rest of the factors that are lower on the list, we inferred that the list was more populated with hard attributes such as location and transportation availability across different price ranges. The negative keyword usages in Table \ref{tab:freq_res_neg} indicate that there were complaints about the lack of a Chinese-friendly environment, but there were more complaints about hard attributes such as the building's age and the distance from other convenient spots. However, most complaints were about the price of the hotel, which included all of the price ranges; therefore, the price was the main concern for Chinese customers with different travel purposes.

>>>>

  Previous research has shown that different cultural backgrounds give rise to different expectations and arguably, different satisfaction factors. We performed a cross-cultural study on the different reactions to the high-standard Japanese hospitality environment between Chinese and Western cultures, to see if these cultures value service over other factors. We compared soft attributes, such as service, with hard attributes, such as location and facilities. We examined the differences in each population's satisfaction and dissatisfaction factors in different price ranges. Taking advantage of the facile data gathering capability enabled by the Web 2.0 technology, we applied Shannon's entropy metric to extract these factors automatically and then used them in a support vector machine to classify a more extensive data set. We then used dependency parsing and part-of-speech tagging to extract the nouns that were tied to ``praising'' adjectives. We found that Chinese tourists are less concerned with hospitality and more with room quality than are Western tourists, whereas, the latter are delighted more by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese-friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

@@

  Japan’s hospitality has been known historically to be of the highest quality. \textit{Omotenashi}, which describes the spirit of Japanese hospitality, with roots in Japanese history and tea ceremony, is celebrated worldwide \cite[][]{al2015characteristics}. Therefore, it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures have different expectations \cite[][]{engel1990}. Thus, it could be theorized that their satisfaction factors should be different. Different cultures could perceive hotels and their hospitality through a different lens.

  In the last couple of decades, the economy of Japan has been affected by an increase in inbound international tourism \cite[][]{jones2009}. A year-on-year growth rate of 19.3\% was observed in 2017, with \num[group-separator={,}]{28691073} inbound tourists \cite[][]{jnto2003-2019}. The tourist population was mostly Asian (86.14\%), and approximately one-fourth of the total (25.63\%) was from China. Western countries, including English-speaking countries in Europe, accounted for 11.4\% of the total, with 7.23\% being countries where English is the official or the de facto national language. The effect of Chinese tourists on international economies is increasing, along with the number of studies on this phenomenon \cite[][]{sun2017}. The tourist market is gradually becoming diverse because of multicultural tourist populations. Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will be varied. Therefore, hotel management must cater to these expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

  However, many tourist-behavior analyses have been performed involving Western subjects. As such, a gap in knowledge existed until recent decades. In studies involving Asian populations in the analysis, Chinese-tourist behaviors have been evaluated most commonly \cite[e.g.][]{liu2019, chang2010, dongyang2015}. The few studies reporting comparisons between Asian and Western tourists’ behaviors \cite[e.g.][]{choi2000} are typically survey- or interview-based, using small samples. These studies, although valid, can have limitations. This gap in research creates a need for large scale cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners account for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul'' customers, spending more than 45\% of their budget on hotels. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and the contrast with the existing literature results.

@@

  The objective of this study is to determine the difference in factors influencing satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels, across several price ranges, using text-mining techniques. We use machine learning to classify the sentiment in texts and natural language processing to study commonly used word pairings. More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction. We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, location, infrastructure, and surrounding real estate. In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.

@@

@@

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the country’s history, and to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}. There is a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, meaning ``The customer is god.'' Some scholars say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century, while other scholars found that it originates in the form of formal banquets in the 7th century \cite[][]{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Presently, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training. High standards are always followed to not fall behind in the competition. In Japanese businesses, including hotels, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language,'' one of the most formal of the Japanese formality syntaxes. They are also trained to bow differently depending on the situation, where a light bow could be used to say ``Please, allow me to guide you.'' Deep bows are used to apologize for any inconvenience the customer could have faced, followed by a very respectful apology. Although the word \textit{omotenashi} can be translated directly as ``hospitality,'' it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}. This hospitality culture permeates every type of business with customer interaction in Japan. A simple convenience shop could express all of these hospitality and service standards, which are not exclusive to hotels.

@@

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}. Western and Chinese customers then have very different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.

@@

    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious. For example, if a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter. However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night. In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed. Then, the same customer might have packed their toiletries, thinking that the amenities might not include those. They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation. This definition of satisfaction does not allow us to examine overall customer satisfaction. However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole. In our study, we consider the definitions in \cite{hunt1975} that satisfaction is a realization of an expectation, and we posit that customers can have different expectations towards different service aspects. Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service. On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.

@@

    Previous research has also focused more on soft attributes, with little focus on hard attributes, if only focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}. However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.

@@

    % Asians vs. Western behavior
    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior, with rapid growth in studies following the year 2007 \cite[][]{sun2017}. This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists. To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even fewer are the number of studies explicitly comparing Chinese and Western tourists. One example is a study by \cite{choi2000}, which found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money. Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities, while Asian tourists were more inclined to enjoy the Karaoke facilities of hotels. Both groups tend to have high expectations for the overall facilities. Another study done by \cite{kim2000} found American tourists to be individualistic and motivated by novelty, while Japanese tourists were collectivist and motivated by increasing knowledge and escaping routine.

    One thing to note with the above Asian vs. Western analyses is that they were performed before 2000 and that they are not Chinese specific. Meanwhile, the current Chinese economic boom is increasing the influx of tourists of this nation. The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations. In turn, if we follow the definition of satisfaction in \cite{hunt1975}, the change in expectations could have influenced their satisfaction factors when traveling. Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports. However, our study of online reviews takes the data that the hotel customers uploaded themselves. This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies. Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.

@@

    On the other hand, our study focuses on Western culture, instead of a single Western country, and Chinese culture clashing with the hospitality environment in Japan, specifically. Japan's importance in this analysis comes from the unique environment of high-grade hospitality that the country presents. In this environment, customers could either hold their satisfaction to this hospitality regardless of their culture, or value other factors more depending on their cultural differences. Our study measures this at a large scale across different hotels in Japan.

@@

    % Studies are not universal.
    Although the studies focusing only on Chinese or Western tourists have a narrow view, their theoretical contributions are valuable. We can see that depending on the study and the design of questionnaires and the destinations, the results can vary greatly. Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other. Since our study uses data mining, each factor's definition is left for hotel customers to decide en masse via their reviews. This means that the factors will be selected through statistical methods alone, instead of being defined by the questionnaire. Our method allows us to find factors that we would not have contemplated. It also avoids enforcing a factor on the mind of study subjects by presenting them with a question that they did not think of by themselves. This large variety of opinions in a well-sized sample, added to the automatic findings of statistical text analysis methods, gives our study an advantage compared to others with smaller samples. This study analyzes the satisfaction and dissatisfaction factors cross-culturally and compares them with the existing literature.

    % Reviewer comparison table
    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and may serve to further highlight our study and its merits. A contrast is shown in Table \ref{tab:lit-rev}. This table shows that older studies were conducted with surveys and had a different study topic. These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}. However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies. Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}. One important difference is the geographical focus of their studies. While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan. The focus on Japan is important because of its top rank in hospitality across all types of businesses. Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent. The number of samples in other text-mining studies is also smaller than ours in comparison. Apart from that, every study has a different text mining method.

@@

    % Sentiment Analysis
    More than only analyzing patterns within the text, researchers have found how to determine the sentiment behind a statement based on speech patterns, statistical patterns, and other methodologies. This method is called sentiment analysis or opinion mining. A precursor of this method was attempted decades ago \cite[][]{stone1966general}. With sentiment analysis, one could use patterns in the text to determine whether a sentence was being said with a positive opinion, or a critical one. This methodology could even determine other ranges of emotions, depending on the thoroughness of the algorithm. Examples of sentiment analysis include ranking products through online reviews \cite[e.g][]{liu2017149, zhang2011}, predicting political poll results through opinions in Twitter \cite[][]{oconnor2010}, and so on. In the hospitality field, it has been used to classify reviewers' opinions of hotels in online reviews \cite[e.g.][]{kim2017362, alsmadi2018}.

    % Machine Learning
    The algorithm used for sentiment analysis in our study is called a Support Vector Machine (SVM), a form of supervised machine learning used for binary classification. Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task. Learning machines can be supervised, as in our study, where the algorithm has manually labeled training data to detect patterns in it and use them to  establish a method for classifying other unlabeled data automatically. Machine learning can also be unsupervised, where there is no pre-labeled data. In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions. Our study calls for a supervised machine since text analysis can be intricate. Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels. Consequently, we teach the machine through previously labeled text samples.

@@

@@

  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}. We then determined the most commonly used words that contribute to positive and negative opinions in a review. We did this using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform an emotional classification of the reviews in large quantities, saving time and resources for the researchers. We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC). We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews. We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels. We observed the frequency of the terms in the dataset to extract the most utilized words in either review. We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}. Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel.

@@

    An SVC is trained to classify data based on previously labeled data, generalizing the data's features by defining a separating (p-1)-dimensional hyperplane in p-dimensional space. Each dimension is a feature of the data in this space. The separating hyperplane, along with the support vectors, divides the multi-dimensional space and minimizes classification error.

    Our study used the SVC classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below. Each training sentence is a data point, a row in the vector \(x\). Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence. The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector. The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle. The bias coefficient \(b\) determines its position.

    During the SVC learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data. These changes to the weight vector are greater for features close to the separating hyperplane. These features have stronger changes because they needed to be taken into account to classify with a minimal error. Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process. Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\). Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications. This equation shows the last value of \(\alpha\) after the end of the cycle.

@@

    Our research questions were related to two issues. Based on research questions \ref{rsq:hospitality} and \ref{rsq:hospitality_both}, the objective of this study was to determine the differences in how Chinese and Western tourists perceive Japanese hotels, whose hospitality and service are influenced by the \textit{omotenashi} culture. We observed the top-ranking positive factors for Chinese tourists across different price ranges, as shown in Table \ref{tab:freq_res_pos}, and specifically the word ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' and its pairings, as shown in Table \ref{tab:adj_zh_pos}. These observations revealed that, while service, cleanliness, and breakfast were praised in most hotels, location was more important when observing the pairings. Including the factors lower on the list, we observed that the list was more populated with hard attributes such as location and transportation availability across different price ranges. The negative keyword usages in Table \ref{tab:freq_res_neg} indicate that there were complaints about the lack of a Chinese-friendly environment, but there were more complaints about hard attributes such as the building's age and the distance from other convenient spots. However, most complaints were about the price of the hotel, which included all of the price ranges; therefore, the price was the main concern for Chinese customers with different travel purposes.
